\documentclass[handout,nooutcomes]{ximera}
%% handout
%% space
%% newpage
%% numbers
%% nooutcomes


\input{../preamble.tex} %% we can turn off input when making a master document

\title{Recitation \#23 - 5.2 Definite Integrals (Teaching Guide)}  

\begin{document}
\begin{abstract}		\end{abstract}
\maketitle


\section*{Warm up:} 
	
	\begin{itemize}
	
	\item  \emph{5 minutes}:  Allow students to work on the warm-up as class begin and then discuss it as a class. Remind the students for part (a) that they can find values for sums with small $n$ by literally just calculating each term and then adding them.  In part (b), review the sigma notation rules.  Point out that there is a big difference between the summation of $i$ and the summation of $1$ and what each means.
	
	
	
	\end{itemize}


\section*{Problem 1:}

	\begin{itemize}
	
	\item  \emph{5 minutes}:  Give the students a few minutes to set up \#1 a as a Riemann sum and then go over this as a class.  
	
	\item  \emph{5 minutes}:  Give the students time to compute the value of the Riemann sum using Sigma Notation rules to get a final expression in terms of $n$.
	
	\item  \emph{5 minutes}:  Go over the computation.  Have a group present if you feel there is time.
	
	\item  \emph{5 minutes}:  Give students a few minutes to take the limit of their expression from part (a) and then go over it as a class.  It is a good idea to remind them that they computed similar limits way back when finding horizontal asymptotes.
	
	\end{itemize}



\section*{Problem 2:}

	\begin{itemize}
	
	\item  \emph{10 minutes}:  Have the students work on \#2 in groups.  If a group finishes early, have them attempt to solve part (b).
		
	\item  \emph{10 minutes}:  Discuss \#2 as a class
			
	\end{itemize}
	
	
	
\section*{Problem 3:}

	\begin{itemize}
	
	\item  \emph{5 minutes}:  Have different groups work on different parts of \#3. If a group finishes their part, they should work on the other parts.
	
	\item  \emph{5 minutes}:  Have students present \#3, or go over as a class if time is running low.
	
	\end{itemize}
	



	
	
	

	
	

	
	
	

	
	
	
















\end{document}