\documentclass[handout,nooutcomes]{ximera}
%% handout
%% space
%% newpage
%% numbers
%% nooutcomes


\input{../preamble.tex} %% we can turn off input when making a master document

\title{Recitation \#21 - 4.7 L'Hospital's Rule and 4.9 Antiderivatives (Teaching Guide)}  

\begin{document}
\begin{abstract}		\end{abstract}
\maketitle


\section*{Warm up:} 
	
	\begin{itemize}
	
	\item  \emph{5 minutes}:  Ask students to think about the warm-up as they are waiting for class to begin.  
	Then discuss the warm-up as a class when class begins.  
	Review the indeterminant forms that may require L'Hospital's Rule.
	%and use the warm-up to review the statement of L'Hospital's Rule and when it can be used.
	
	
	
	\end{itemize}


\section*{Problem 1:}

	\begin{itemize}
	
	\item  \emph{5 minutes}:  Use 1(a) as a demonstration to model to the students what they are supposed to be doing.  Then give the students some time to try to determine the form for each limit.
	
	\item  \emph{5 minutes}:  Go over the form for each limit, explaining the reasoning to get the answer. Discuss the use of arrow or limit notation instead of using an equals sign inappropriately.  
	%It would be nice to have students present here, but there likely won’t be enough time.
	
	\end{itemize}



\section*{Problem 2:}

	\begin{itemize}
	
	\item  \emph{10 minutes}:  Split the problems up between the groups for \#2 and give them time to work.  Be prepared for students to be confused on why L'Hospital's Rule is not working for them on problem 2(a).
		
	\item  \emph{10 minutes}:  Have students present their solutions from \#2
			
	\end{itemize}
	
	
	
\section*{Problem 3:}

	\begin{itemize}
	
	\item  \emph{5 minutes}:  Split the parts of \#3 between the groups.  Students will have the most trouble with $\frac{7}{t}$ and $\frac{5}{11+t^2}$  
	
	\item  \emph{5 minutes}:  Go over the answers. Allow students to present if time permits.
	
	\end{itemize}
	


\section*{Problem 4:}

	\begin{itemize}
	
	\item  \emph{5 minutes}:  Allow students to work on \#4 in groups.  
		
	\item  \emph{5 minutes}:  As a class, go over \#4.
	\end{itemize}	
	
	
	

	
	

	
	
	

	
	
	
















\end{document}