\documentclass[handout,nooutcomes]{ximera}
%% handout
%% space
%% newpage
%% numbers
%% nooutcomes


\input{../preamble.tex} %% we can turn off input when making a master document

\title{Recitation \#10 - 3.5 Derivatives of Trig Functions (Teaching Guide)}  

\begin{document}
\begin{abstract}		\end{abstract}
\maketitle


\section*{Warm up:} 
	
	\begin{itemize}
	
	\item  \emph{5 minutes}:  Discuss the warm up as a class.  I always like to (very) quickly mention to my class the fact that $\sin^{(4)}(x) = \sin(x)$ and $i^4 = i$ are very related, but I certainly understand if you want to skip this and head to the problems.	
	\end{itemize}


\section*{Problem 1:}

	\begin{itemize}
	
	\item  \emph{10 minutes}:  Allow students to work on \#1 in groups.  Have different groups do parts $a$, $b$, and $c$.  If they finish early, they can work on the other parts.
	
	\item  \emph{5 minutes}:  Allow students to present their solutions to \#1
			
	\end{itemize}
	
	
	
\section*{Problem 2:}

	\begin{itemize}
	
	\item  \emph{10 minutes}:  Allow about 7 minutes for different groups to work on parts $a$ and $b$ in groups.  Then give them a few minutes to present their solutions.
	
	\item  \emph{15 minutes}:  Allow about 10 minutes for different groups to work on parts $c$ and $d$ in groups.  Then give them about 5 minutes to present their solutions.
	
	\end{itemize}
	


\section*{Problem 3:}

	\begin{itemize}
	
	\item \emph{5 minutes}:  Allows students to work on \#3 in groups. 
	
	\item \emph{5 minutes}:  Allow a group to present their solution to problem \#3.
	
	\end{itemize}	
	
	
	
	
	

	
	
	

	
	
	
















\end{document}