\documentclass[handout,nooutcomes]{ximera}
%% handout
%% space
%% newpage
%% numbers
%% nooutcomes


\input{../preamble.tex} %% we can turn off input when making a master document

\title{Recitation \#15 - 4.1 Maxima and Minima (Teaching Guide)}  

\begin{document}
\begin{abstract}		\end{abstract}
\maketitle


\section*{Warm up:} 
	
	\begin{itemize}
	
	\item  \emph{5 minutes}:  Ask students to think about the Warm-Up as they are waiting for class to begin.  Then discuss the warm-up as a class when class begins.
	
	
	
	\end{itemize}


\section*{Problem 1:}

	\begin{itemize}
	
	\item  \emph{10 minutes}:  Allow students to work on \#1 in groups.  I think it is best if each group attempts all four parts, as that way they can think about the differences between differentiating the different functions.
	
	\item  \emph{5 minutes}:  Let a group present their solution(s).
	
	\end{itemize}



\section*{Problem 2:}

	\begin{itemize}
	
	\item  \emph{5 minutes}:  Allow students to work on \#2 in groups.  Split the two parts between the groups.
		
	\item  \emph{5 minutes}:  Let groups present their solutions to each part.
			
	\end{itemize}
	
	
	
\section*{Problem 3:}

	\begin{itemize}
	
	\item  \emph{10 minutes}:  Allow students to work on \#3 in groups.  
	
	\item  \emph{5 minutes}:  Allow a group to present their solutions to \#3.
	
	\end{itemize}
	


\section*{Problem 4:}

	\begin{itemize}
	
	\item  \emph{5 minutes}:  Allow students to work on \#4 in groups.  
		
	\item  \emph{5 minutes}:  Discuss the various parts to problem 4 as a class.  The solutions contain a cute story which makes the problem a little more tangible.  I read it to my class last semester and I think they both enjoyed it (in a humerous way) and it helped them understand what is going on as well.  But feel free to skip the story if you do not like it.	
	\end{itemize}	
	
	
	

	
	

	
	
	

	
	
	
















\end{document}